Figures

### 2020-02-11 manuscript/figures.Rmd
adjust fig dimensions

![Diagram showing our expectation that slope-based models of lake depth will under predict true depth in convex lakes (left) and over predict true depth in concave lakes (right)](../figures/lake_shape.pdf){width=100%}

>>>>

![Diagram showing our expectation that slope-based models of lake depth will under predict true depth in convex lakes (left) and over predict true depth in concave lakes (right)](../figures/lake_shape.pdf){width=85%}
